### 2019-06-12 2-Chapters/1-Chapter/chapter1.tex
Done

% FIXME
\newpage

@@

% =============================================================================
\paragraph{Publications in international conferences with proceedings}

@@

% =============================================================================
\paragraph{Demonstration in international conferences}

@@

% =============================================================================
\paragraph{French language conference with proceedings}
% \textbf{Submitted works}

@@

% =============================================================================
\paragraph{In progress works waiting for a new submission}

>>>>

% WARNING
\newpage

@@

We conclude this chapter with a list of publications published during this PhD.
All the publications are published on HAL (see the \href{https://hal.archives-ouvertes.fr/}{\texttt{HAL.Archives-Ouvertes.fr}} website),
and the complete list can be found on
\href{https://cv.archives-ouvertes.fr/lilian-besson/}{\texttt{CV.Archives-Ouvertes.fr/lilian-besson}}.

% =============================================================================
\subsection*{Publications in international conferences with proceedings}

@@

% =============================================================================
\subsection*{Demonstration in international conferences}

@@

% =============================================================================
\subsection*{French language conference with proceedings}
% \textbf{Submitted works}

@@

% =============================================================================
\subsection*{In progress works waiting for a new submission}

### 2019-06-12 2-Chapters/2-Chapter/chapter2.tex
\vfill{} before \minitoc at beginning of all Chapters
Done

\TODOL{Enlever ça, juste une phrase qui dit "on le fait plus tard".}
We find more interesting to study $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, the sum of the switching costs of the $M$ players in a multi-players bandit game (if player $j$ uses algorithm $\cA_j$ for $j=1,\dots,M$). Indeed in this case it is possible that the players attain a logarithmic centralized regret, by following an efficient centralized or decentralized algorithm, while still suffering from a linear switching cost.
%
It is very satisfying to obtain a logarithmic switching cost for our algorithm \MCTopM-\klUCB{} in Chapter~\ref{chapter:5}, even if minimizing the switching cost was not one of our objective, and the bound we obtain on $SC^{\cA_1,\dots,\cA_M}(T)$ is just a consequence of our proof of the control we give on the regret $R^{\cA}(T)$.
% - Switching cost? \cite{modiDemo2016} \cite{Koren17}
On a more experimental note, it was shown in \cite{modiDemo2016} that the previous state-of-the-art policy for multi-players bandits, \rhoRand, could be tuned to run in batches\footnote{~The batch bandit setting implies that all players use the same decisions for instance for $50$ consecutive times, and update their decisions only once every $50$ time steps. For more details, see \cite{modiDemo2016} for experiments on the multi-players case, or \cite{perchet2016,gao2019batched,kolnogorov2019multi} for theoretical developments on the single-player case.}, in order to reduce by a certain multiplicative factor its switching cost while only adding an additive factor on its regret. While such ideas can interest a practitioner, they does not change the asymptotic behavior of $SC^{\cA_1,\dots,\cA_M}(T)$, which is $\Theta(\log(T))$ for any efficient policy.

@@

Instead of using a confidence radius $\xi_k(t)$ based on Hoeffding's inequality,
the \klUCB{} algorithm rather use a specific concentration inequality for the considered exponential family, such as Chernoff-Hoeffding for Gaussian (or sub-Gaussian) rewards.
It yields improved upper confidence bounds (\ie, with smaller $\xi_k(t)$) that are based on Kullback-Leibler divergence.
The indexes are computed as follows, for an exploration function $f(t)$
that is typically chosen as $f(t) \eqdef \log(t)+3\log(\log(t))$ for the theoretical analyses,
and $f(t) \eqdef \log(t)$ in practice.
The constant $c>0$ is usually chosen as $c = 1$.
\begin{align}\label{eq:klUCB_index}
    U_k^{\klUCB}(t) \eqdef \sup\limits_{q \in [0, 1]} \left\{ q : \KL\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{c f(t}{N_k(t)} \right\}.
\end{align}

@@

% ----------------------------------------------------------------------------
\textbf{Hybrid policies.}
%
As explained before, in the last few years, the MAB research community has been interested in finding algorithms which achieves both a problem-dependent logarithmic and a minimax upper-bounds.
We present here some solutions that are index-based (see Algorithm~\ref{algo:2:indexPolicy}).
The first example is MOSS from \cite{Audibert2009minimax}, or \KLUCBpp{} in \cite{Menard17},
and they use the following indexes:
\begin{align}\label{eq:2:indexes_for_MOSS_klUCBpp}
    U^{\mathrm{MOSS}}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \frac{\log\left(\frac{t}{K N_k(t)}\right)}{N_k(t)} } \right). \\
    U^{\KLUCBpp}_k(t) & \eqdef \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{g(N_k(t), T, K)}{N_k(t)} \right\}.
\end{align}
%
If we denote $g(t, T, K) = \log^+(y(t) (1 + \log^+(y(t))^2))$, and $y(t) = \frac{T}{K t}$, with $\log^+(x) = \max(0, \log(x))$.

@@

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proven to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses a modified version of the indexes of the \klUCB$^+$ algorithm (see \cite{Honda2019} for more details), for arms that are not sampled much, and a modified version of the indexes of the MOSS$^+$ algorithm, for the other arms.
To detail this, first let $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch use the index defined as follows:
%
\begin{align}\label{eq:2:indexes_for_klUCBswitch}
    U^{\mathrm{MOSS}+}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \frac{\log\left(\frac{T}{K N_k(t)}\right)}{N_k(t)}} \right). \\
    U^{\KLUCB+}_k(t) & \eqdef \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{\log(\frac{T}{K N_k(t)})}{N_k(t)} \right\} \\
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align}

>>>>

\TODOL{Enlever ça, juste une phrase qui dit "on le fait plus tard".}
We find more interesting to study $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, the sum of the switching costs of the $M$ players in a multi-players bandit game (if player $j$ uses algorithm $\cA_j$ for $j=1,\dots,M$). Indeed in this case it is possible that the players attain a logarithmic centralized regret, by following an efficient centralized or decentralized algorithm, while still suffering from a linear switching cost.
%
It is very satisfying to obtain a logarithmic switching cost for our algorithm \MCTopM-\klUCB{} in Chapter~\ref{chapter:5}, even if minimizing the switching cost was not one of our objective, and the bound we obtain on $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$ is just a consequence of our proof of the control we give on the regret $R^{\cA}(T)$.
% - Switching cost? \cite{modiDemo2016} \cite{Koren17}
On a more experimental note, it was shown in \cite{modiDemo2016} that the previous state-of-the-art policy for multi-players bandits, \rhoRand, could be tuned to run in batches\footnote{~The batch bandit setting implies that all players use the same decisions for instance for $50$ consecutive times, and update their decisions only once every $50$ time steps. For more details, see \cite{modiDemo2016} for experiments on the multi-players case, or \cite{perchet2016,gao2019batched,kolnogorov2019multi} for theoretical developments on the single-player case.}, in order to reduce by a certain multiplicative factor its switching cost while only adding an additive factor on its regret. While such ideas can interest a practitioner, they does not change the asymptotic behavior of $\mathrm{SC}^{\cA_1,\dots,\cA_M}(T)$, which is $\Theta(\log(T))$ for any efficient policy.

@@

Instead of using a confidence radius $\xi_k(t)$ based on Hoeffding's inequality,
the \klUCB{} algorithm rather use a specific concentration inequality for the considered exponential family, such as Chernoff-Hoeffding for Gaussian (or sub-Gaussian) rewards.
It yields improved upper confidence bounds (\ie, with smaller $\xi_k(t)$) that are based on Kullback-Leibler divergence.
The indexes are computed as follows, for an exploration function $f(t)$
that is typically chosen as $f(t) \eqdef \log(t)+3\log(\log(t))$ for the theoretical analyses,
and $f(t) \eqdef \log(t)$ in practice.
The constant $c>0$ is usually chosen as $c = 1$.
\begin{align}\label{eq:klUCB_index}
    U_k^{\klUCB}(t) \eqdef \sup\limits_{q \in [0, 1]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{c f(t}{N_k(t)} \right\}.
\end{align}

@@

% ----------------------------------------------------------------------------
\textbf{Hybrid policies.}
%
As explained before, in the last few years, the MAB research community has been interested in finding algorithms which achieves both a problem-dependent logarithmic and a minimax upper-bounds.
We present here some solutions that are index-based (see Algorithm~\ref{algo:2:indexPolicy}).
The first example is MOSS from \cite{Audibert2009minimax}, or \KLUCBpp{} in \cite{Menard17},
and they use the following indexes:
\begin{align}\label{eq:2:indexes_for_MOSS_klUCBpp}
    U^{\mathrm{MOSS}}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \frac{\log\left(\frac{t}{K N_k(t)}\right)}{N_k(t)} } \right). \\
% \end{align}
% \begin{align}\label{eq:2:indexes_for_MOSS_klUCBpp2}
    U^{\KLUCBpp}_k(t) & \eqdef \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{g(N_k(t), T, K)}{N_k(t)} \right\}.
\end{align}
%
If we denote $g(t, T, K) = \log^+(y(t) (1 + \log^+(y(t))^2))$, and $y(t) = \frac{T}{K t}$, with $\log^+(x) = \max(0, \log(x))$.

@@

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proven to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses a modified version of the indexes of the \klUCB$^+$ algorithm (see \cite{Honda2019} for more details), for arms that are not sampled much, and a modified version of the indexes of the MOSS$^+$ algorithm, for the other arms.
To detail this, first let $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch use the index defined as follows:
\[
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\]

If the two indexes $U^{\KLUCB+}_k(t)$ and $U^{\mathrm{MOSS}+}_k(t)$ are defined by

% \vspace*{-20pt}   % FIXME??
\begin{align*}
    U^{\mathrm{MOSS}+}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \frac{\log\left(\frac{T}{K N_k(t)}\right)}{N_k(t)}} \right). \\
% \end{align*}
% \begin{align*}
    U^{\KLUCB+}_k(t) & \eqdef \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{\log(\frac{T}{K N_k(t)})}{N_k(t)} \right\} \\
% \end{align*}
% \begin{align*}
    % U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
    %     U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
    %     U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    % \end{cases}.
\end{align*}
